The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-04-12 paper/paper.tex
add new figs

\begin{figure}[htbp]
	% \centering
	\includegraphics[width=1\linewidth]{results/funbins_nz.pdf}
	\caption{The tomographic $n(z)$ values generated by the winning method in the challenge, {\sc funbins},
		generating nine bins with the CosmoDC2 data.
		The upper panel shows results for the method applied to $riz$ bands, and the middle on $griz$. The
		increased spread and overlap of the bins in the middle panel decreases the overall constraining
		power and signal-to-noise.  The lower panel is for comparison and is not part of the challenge,
		and illutrates results using all the $ugrizy$ bands.}
	\label{fig:funbin_nz}
\end{figure}

@@

For comparison, we also show results using all six LSST bands, $ugrizy$; these could not be used
with the metacalibration method. The improvement in the sharpness of the bins is noticeable but not large,
and does not translate into large increases in the figures of merit: the DETF score for CosmoDC2
is 169.7, barely higher than the score for $griz$, and this is also true for other metrics.   While this is only a general indication and not a thorough exploration, it is encouraging.

>>>>

\begin{figure}[htbp]
	% \centering
	\includegraphics[width=1\linewidth]{results/nzbinned_dc2_funbins.pdf}
	\caption{The tomographic $n(z)$ values generated by the winning method in the challenge, {\sc funbins},
		generating nine bins with the CosmoDC2 data.
		The upper panel shows results for the method applied to $riz$ bands, and the middle on $griz$. The
		increased spread and overlap of the bins in the middle panel decreases the overall constraining
		power and signal-to-noise.  The lower panel is for comparison and is not part of the challenge,
		and illutrates results using all the $ugrizy$ bands.}
	\label{fig:funbin_nz}
\end{figure}

@@

For comparison, we also show results using all six LSST bands, $ugrizy$; these could not be used
with the metacalibration method. The improvement in the sharpness of the bins is noticeable but not large.
We quantify this in Figure \ref{fig:overlap}, which shows the fraction of objects assigned to each
bin that are actually in another redshift range, together with the total fraction of mis-assigned galaxies 
over all the bins, for each set of bands. This illustrates how adding the $g$ band improves the assigment
for almost every pair of bins, and reduce the total mis-assigned fraction by a factor of three to the 
point where a significant majority of galaxies are in the right bin.  Further adding the remaining $u$ and $y$
bands improves the assignment in a way that is smaller in both relative and absolute terms.
This latter addition also does not translate into large increases in the figures of merit: the 
DETF score for CosmoDC2 is 169.7, barely higher than the score for $griz$, and this is also true for other 
metrics.   While this is only a general indication and not a thorough exploration, it is encouraging.

\begin{figure*}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/nzoverlap_dc2_funbins.pdf}
\caption{The fraction of total objects mis-assigned from each bin to each other bin in the winning 
\textsc{funbins} method for different choices of bands.  The $x$- and $y$-axes show tomographic bin indices, 
and the color represents the fraction of objects (compared to the total number in the challenge) that are 
mis-assigned from each bin to each other.  The total-overlap figure gives the total fraction of objects
that are mis-assigned over all bins, and is the sum of all the values.}
\label{fig:overlap}
\end{figure*}
